### 2015-02-08 docs/report/initialization.tex
Initial content on code sharing between ui and workers
Array sharing documentation

As explained in the standard \cite{w3c-ww} \textit{"Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

These were the results:
\bmchart{Evaluating the inefficiency of cold starting a Web Worker}{../../spikes/2.1.1/newVsPreExistent}

>>>>

As explained in the standard \cite{w3c-ww} \textit{``Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

The results for it are displayed in Figure~\ref{fig:new-vs-pre}.
\img{Evaluating the inefficiency of cold starting a Web Worker}{../../spikes/2.1.1/newVsPreExistent}{fig:new-vs-pre}
